{\selectlanguage{english}
\foreignlanguage{english}{
The whole experiment has been carried out with free open source. In addition, I just needed a computer to run all the pieces locally and no more infrastructure was required. Therefore, the experiment was quite cheap.

Nevertheless, we can assume this proof of concept is performed by a company and estimate the budget. To do so, we will have to buy the computer and pay the salary of the developer and training resources. 

On the one hand, the computer could be anyone with proper power which is valued at around \textbf{\euro{800}} with taxes included. On the other hand, the time spent on developing the experiment is around 600 hours in my case, 30 weeks working 20 hours per week. Moreover, we may assume a net salary for a full stack average developer of around \euro{15} per hour. Taking into account that the 30\% is subject to the IRPF tax, to maintain such a net salary we need to pay a gross salary of \euro{21.42} per hour. In conclusion, if we multiply the 600 hours of work by the \euro{21.42} per hour we obtain then the total salary sums up to \textbf{\euro{12857.15}}. Finally, the training to learn how to develop smart contracts and an off-blockchain backend has a price of \textbf{\euro{40}} altogether. The table \ref{tab:budget} collects all the expenses aforementioned.

\begin{table}[h!]
\centering
\caption[Budget]{ \footnotesize This table gathers the different concepts that a company should pay to carry out the project as a proof of concept}
\label{tab:budget}
\footnotesize{
\begin{tabular}{||c c ||} 
 \hline
 Concepts & Cost \\ [0.5ex] 
 \hline\hline
  Computer & \euro{800}  \\
 Wage & \euro{12857.15} \\ 
 Training & \euro{40}  \\ [1ex] 
 \hline
 Total & \euro{13697.15} \\ [0.5ex] 
 \hline
\end{tabular}
}
\end{table}

}
}
