\makeglossaries

\newglossaryentry{tip}{
name=tip,
description={The priority fee (tip) incentivizes validators to include a transaction in the block. Without tips, validators would find it economically viable to mine empty blocks, as they would receive the same block reward. Small tips give validators a minimal incentive to include a transaction. For transactions to be preferentially executed ahead of other transactions in the same block, a higher tip can be added to try to outbid competing transactions}
}

\newglossaryentry{gossip}{
name=Gossip protocol,
description={
The Gossip protocol is a protocol that allows designing highly efficient, secure and low latency distributed communication systems Peer-2-Peer(P2P)}
}

\newglossaryentry{economy-of-scale}{
name=economy of scale,
description={A proportionate saving in costs gained by an increased level of production}
}

\newglossaryentry{51-attack}{
name=51\% attack,
description={A 51\% attack is an attack on a distributed network by a group of dishonest nodes who control more than 50\% of the network's mining node rate. Owning 51\% of the nodes on the network theoretically gives the controlling parties the power to alter the state as desired
}
}

\newglossaryentry{json}{
name=JSON,
description={A JSON (JavaScript Object Notation) is a simple text formatting used for data communication}
}

\newglossaryentry{orm}{
name=ORM,
description={Object Relational Mapping (ORM) is a technique that creates a bridge between object-oriented programs and relational databases.}
}

\newglossaryentry{nonce}{
name=nonce,
description={A nonce is an arbitrary number used only once in a cryptographic communication created randomly or pseudo-randomly.}
}

\newglossaryentry{dom}{
name=dom,
description={The Document Object Model (DOM) is a programming interface for web documents. It represents the page so that programs can change the document structure, style, and content.}
}

\newglossaryentry{api}{
name=API,
description={API stands for application protocol interface, which is a set of definitions and protocols for building and integrating application software in other to communicate with other services and products without having to know how are they implemented.}
}


\newacronym{pow}{PoW}{Proof of Work}
\newacronym{pos}{PoS}{Proof of Stake}
\newacronym{evm}{EVM}{Ethereum Virtual Machine}
\newacronym{eth}{ETH}{Ether}
\newacronym{abi}{ABI}{Application Binary Interface}
\newacronym{ui}{UI}{User Interface}
\newacronym{ux}{UX}{User Experience}